Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/4_results.tex
First pass of fixes.
Fix the other table.

\begin{table}
	\centering
	\small
	\setlength{\tabcolsep}{0.75em}
	\begin{tabular}{c c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
		Kasthuri & 610 / 23506 & 556 / 4921 & 214 & 160 \\
		FlyEM Vol. 1 & 304 / 15949 & 212 / 4578 & 105 & 13 \\
		FlyEM Vol. 2 &  298 / 17614 & 197 / 4366 & 120 & 19 \\ \hline
	\end{tabular}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23506) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
	\label{table:skeletonization}
\end{table}

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
On average in our datasets we correctly merge \TODO{XX} of the non-adjacent segments.

There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results} shows two such cases. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average 146 such examples in our datasets.

\begin{figure}[t!]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}	
		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
	\end{minipage}
	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
	\label{fig:skeleton-results}
\end{figure}

%\subsection{CNN Classification Results}
\noindent\textbf{Edge Weight Learning}
We first evaluate the effectiveness of inference augmentation.
%\subsubsection{Inference Augmentation}
%\noindent\textbf{Inference Augmentation.}
Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

@@

%\subsubsection{Generalization to Other Datasets}
%\noindent\textbf{Generalization to Other Datasets.}
Our neural network does not take as input the images or affinities so we can transfer network weights from one dataset to the next.
The classification results are reasonable on the FlyEM datasets despite the fact that the data varies in resolution and even animal type from the training set.

%\subsection{Graph Optimization Results}
\noindent\textbf{Graph Partition}
The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and ``lifted'' multicut formulations.
These results correspond to $\beta = 0.5$ (Sec.~\ref{sec:edge-weights}). 
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
The ``lifted'' variant further accentuates this trend of increasing precision and accuracy at the expense of recall. 
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.

\begin{table}[h]
	\centering
	\small
	\setlength{\tabcolsep}{0.3em}
	\begin{tabular}{c c c c | c c c} \hline
		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri  & 7.56\% & -3.83\% & 0.89\% & -5.67\% & -2.15\% & -1.03\% \\
		FlyEM Vol. 1 & 4.50\% & -4.24\% & 0.26\% & -1.52\% & -2.97\% & -0.16\%  \\
		FlyEM Vol. 2 & 5.54\% & -1.38\% & 0.26\% & -8.65\% & -2.75\% & -0.54\%\\ \hline
	\end{tabular}
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy.}
	\label{table:multicut}
\end{table}

@@

\subsection{Computational Performance}
%\subsubsection{System} 
\noindent\textbf{System}
All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. All code is written in Python and will be freely available upon paper decision. We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.

>>>>

\begin{table}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23506) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
\resizebox{\linewidth}{!}{
	\begin{tabular}{c c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
		Kasthuri & 610 / 23506 & 556 / 4921 & 214 & 160 \\
		FlyEM Vol. 1 & 304 / 15949 & 212 / 4578 & 105 & 13 \\
		FlyEM Vol. 2 &  298 / 17614 & 197 / 4366 & 120 & 19 \\ \hline
	\end{tabular}
}
	\centering
	\label{table:skeletonization}
\end{table}

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
On average in our datasets we correctly merge \TODO{XX} of the non-adjacent segments. 
\begin{figure}[t!]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}	
		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
	\end{minipage}
	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
	\label{fig:skeleton-results}
\end{figure}
There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results} shows two such cases. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average 146 such examples in our datasets.
\\~\\
\noindent\textbf{Edge Weight Learning}
We first evaluate the effectiveness of inference augmentation.
%\subsubsection{Inference Augmentation}
%\noindent\textbf{Inference Augmentation.}
Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

@@

%\subsubsection{Generalization to Other Datasets}
%\noindent\textbf{Generalization to Other Datasets.}
Our neural network does not take as input the images or affinities so we can transfer network weights from one dataset to the next.
The classification results are reasonable on the FlyEM datasets despite the fact that the data varies in resolution and even animal type from the training set.
\\~\\
%\subsection{Graph Optimization Results}
\noindent\textbf{Graph Partition}
The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and ``lifted'' multicut formulations.
These results correspond to $\beta = 0.5$ (Sec.~\ref{sec:edge-weights}). 
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
The ``lifted'' variant further accentuates this trend of increasing precision and accuracy at the expense of recall. 
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.

\begin{table}[h]
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy.}
	\centering
\resizebox{\linewidth}{!}{
	\begin{tabular}{c c c c | c c c} \hline
		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri  & 7.56\% & -3.83\% & 0.89\% & -5.67\% & -2.15\% & -1.03\% \\
		FlyEM Vol. 1 & 4.50\% & -4.24\% & 0.26\% & -1.52\% & -2.97\% & -0.16\%  \\
		FlyEM Vol. 2 & 5.54\% & -1.38\% & 0.26\% & -8.65\% & -2.75\% & -0.54\%\\ \hline
	\end{tabular}
}
	\label{table:multicut}
\end{table}

@@

\subsection{Computational Performance}
%\subsubsection{System} 
\noindent\textbf{System}
All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. All code is written in Python and is freely available (link omitted for review). We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.

### 2018-03-14 papers/eccv2018/5_conclusions.tex

There is significant room for additional research and improvements. We can augment the graph with additional information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc. This would allow us to enforce additional biological constraints during graph partitioning. For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections. An augmented graph would also be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. Finally, we believe that the benefits of top-down enhancements from graph optimization can extend beyond connectomics to other domains, such as medical image segmentation.

>>>>

In the future, these methods can be adjusted to apply additional domain constraints. 
We can augment the graph with more information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc. 
This would allow us to match other biological constraints during graph partitioning. 
For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections. 
An augmented graph would also be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. 
Finally, we believe that the benefits of top-down enhancements from graph optimization can extend beyond connectomics to other domains, such as medical image segmentation.
